Homeless Populations in Toronto

### 2022-02-05 outputs/paper/paper.Rmd
testing

```{r setup, include=FALSE}
install.packages("opendatatoronto")
library(opendatatoronto)
library(tidyverse)
library(tidyr)
library(knitr)
library(janitor)
library(lubridate)
```

@@

Our data is of penguins (Figure \@ref(fig:bills)).

```{r bills, fig.cap="Bills of penguins", echo = FALSE}

@@

# Model

\begin{equation}
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}  (\#eq:bayes)
\end{equation}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
# install.packages("opendatatoronto")
library(opendatatoronto)
library(tidyverse)
library(tidyr)
library(knitr)
library(janitor)
library(lubridate)
```

@@

@@
